PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
more fig caption

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets (\cref{pfp}) in blue.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs (\cref{def:sfp}).]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples where $u\b v$, where $u,v\in B$ can freely move around and
  their neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\hfill
\subfloat[An instance of \cref{lem:weak}.]{
\includegraphics[width=0.30\textwidth]{fig/simple.pdf}%
\label{fig:simple}
}
\hfill
\subfloat[Examples of blocking sets (\cref{pfp}), preventing $u\b v$.]{
\includegraphics[width=0.6\textwidth]{fig/blocking-set.pdf}%
\label{fig:blocking}
}
\hfill
\\
\subfloat[Examples of strongly fixed pairs (\cref{def:sfp}).]{
\includegraphics[width=0.9\textwidth]{fig/strongly-fixed.pdf}%
\label{fig:strongly-fixed}
}
%% \subfloat[]{
%% \includegraphics[width=0.33\textwidth]{fig/gluing.pdf}%
%% \label{fig:gluing}
%% }
\caption{
  Various examples where $u$ must come before $v$ ($u\b v$), where $u,v\in B$ can freely move around and
  their neighbours in $A$ (on the dashed line) have fixed positions.}%
\label{fig}
\end{figure}
